Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/sections/Overview.tex
S2.3 adding nature workaround in c++

\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}

We have seen that hierarchical dispatch can dynamically find the latest implementation of a method from one path (or branch). But when
several branches are merged by triangle inheritance, there is usually demand for updating them separately. For example, someone plans to
reuse the other features of \lstinline|DrawableLoggingDeck|, but updates the \lstinline|draw| from \lstinline|Drawable| by setting the canvas
invisible. Unfortunately in traditional models, the merged branches cannot be separately overridden any longer, since overriding
will hide all branches and break coexistence. Modifying existing code is again unsatisfactory as it affects modularity.\\

\noindent\textbf{Our solution:} an additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck2 extends DrawableLoggingDeck {
  void draw() override Drawable {
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(false);
    ...
  }
}
// main program
DrawableLoggingDeck2 d = new DrawableLoggingDeck2();
d.Drawable::draw()      // calling draw in DrawableLoggingDeck2
\end{lstlisting}\vspace{3pt}
\textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
In contrast, \lstinline|DrawableLoggingDeck2| defines a ``hierarchical overriding'' method. The difference is that traditional overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.

In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch. A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity. The compiler is supposed to forbid that during compile time.

Two rules for hierarchical overriding: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature. For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|LoggingDeck.draw|, while \lstinline|Deck.draw| is already covered. It does not really make sense to refine an old branch.

>>>>

\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
We have seen that hierarchical dispatch can dynamically find the latest implementation of a method from one path (or branch). But when
several branches are merged by triangle inheritance, there is usually demand for updating them separately. For example, someone plans to
reuse the other features of \lstinline|DrawableSafeDeck|, but updates the \lstinline|draw| from \lstinline|Drawable| by drawing a rectangle representing deck. Unfortunately in traditional models, the merged branches cannot be separately overridden any longer, since overriding
will hide all branches and break coexistence. Modifying existing code is again unsatisfactory as it affects modularity. The nature way to work around the problem is to define a new component \lstinline|Drawable2| and change the class hierarchy:
\begin{lstlisting}
interface Drawable2 extends Drawable {
  void draw() {
    JFrame frame = new JFrame("Canvas");
    frame.setSize(600, 600);
    frame.getContentPane().setBackground(Color.red);
    frame.getContentPane().add(new Square(10,10,100,100));
    ....
  }
}
interface DrawableSafeDeck extends Drawable2, SafeDeck {}
\end{lstlisting} 
The drawabck of the workaround is obvious: it breaks the existing hierarchy and changes the old code.

\noindent\textbf{Our solution:} an additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
\vspace{3pt}\begin{lstlisting}
interface DrawableSafeDeck extends Drawable, SafeDeck {
  void draw() override Drawable {
    JFrame frame = new JFrame("Canvas");
    frame.setSize(600, 600);
    frame.getContentPane().setBackground(Color.red);
    frame.getContentPane().add(new Square(10,10,100,100));
    ...
  }
}
// main program, calling draw in DrawableSafeDeck
((Drawable)new DrawableSafeDeck()).draw(); 
\end{lstlisting}\vspace{3pt}

\textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
In contrast, \lstinline|DrawableSafeDeck2| defines a ``hierarchical overriding'' method. The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.

In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch. A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck2|, it leads to ambiguity. The compiler is supposed to forbid that during compile time.

Two rules for hierarchical overriding: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature. For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered. It does not really make sense to refine an old branch.
